Automated Lensing Learner - I: An automated Strong Lensing Identification Pipeline

### 2017-03-22 ms.tex
Added Wentao's affiliation

\author{Camille Avestruz\altaffilmark{1-3,$\dagger$}\thanks{E-mail:
    avestruz@uchicago.edu}, Nan Li\altaffilmark{2-4}, Matthew Lightman\altaffilmark{5}, Thomas E.~Collett\altaffilmark{6}}

\affil{
$^1${Enrico Fermi Institute, The University of Chicago, Chicago, IL 60637 U.S.A.}\\
$^2${Kavli Institute for Cosmological Physics, The University of Chicago, Chicago, IL 60637 U.S.A.}\\
$^3${Department of Astronomy \& Astrophysics, The University of Chicago, Chicago, IL 60637 U.S.A.};\\
$^4${High Energy Physics Division, Argonne National Laboratory,
Lemont, IL 60439};\\
$^5${Digital Intelligence, JPMorgan Chase, Chicago, IL 60603 U.S.A.};\\
$^6${Institute of Cosmology and Gravitation, University of Portsmouth, Burnaby Rd, Portsmouth, PO1 3FX, UK};\\
$^\dagger${Provost's Postdoctoral Scholar at the University of Chicago}\\
  \href{mailto:avestruz@uchicago.edu}{avestruz@uchicago.edu}\\
}

@@

% Convolutional and residual
\wording{The most advanced use of neural networks for strong lensing
  classification operate directly in image space.
  \citep{petrillo_etal17} used mock Kilo Degree Survey data to train
  convolutional neural networks, with a training set size of six
  million images. \citet{lanusse_etal17} used state-of-the-art
  residual learning to also work directly in the image space with
  minimal image pre-processing.  A major strength of the
  \citet{lanusse_etal17} implementation is that residual learning has
  been found to be easier to train in deep neural networks, and can
  outperform implementations of convolutional neural networks.}

@@

In a forthcoming paper, we will discuss how class imbalance, or
differences between the lens-model parameter distributions in the
training and test sets affect model performance and will explore a
method to correct for this.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure*}[t]
  \centering 
  \mbox{
    \subfigure{\includegraphics[width=.66\columnwidth,trim=13 0 10 0,
        clip]{figures/lens_parameter_dependence/HST_Magnification_Velocity_Dispersion.pdf}}\hfill
    \subfigure{\includegraphics[width=.66\columnwidth,trim=13 0 10 0,
        clip]{figures/lens_parameter_dependence/LSST10_Magnification_Velocity_Dispersion.pdf}}\hfill
    \subfigure{\includegraphics[width=.66\columnwidth,trim=13 0 10 0,
        clip]{figures/lens_parameter_dependence/LSST1_Magnification_Velocity_Dispersion.pdf}\hfill}
  }\\ 
  \mbox{
    \subfigure{\includegraphics[width=.66\columnwidth,trim=13 0 10 0,
        clip]{figures/lens_parameter_dependence/HST_Magnification_z.pdf}}\hfill
    \subfigure{\includegraphics[width=.66\columnwidth,trim=13 0 10 0,
        clip]{figures/lens_parameter_dependence/LSST10_Magnification_z.pdf}}\hfill
    \subfigure{\includegraphics[width=.66\columnwidth,trim=13 0 10 0,
        clip]{figures/lens_parameter_dependence/LSST1_Magnification_z.pdf}\hfill}
  }\\ 
\caption{Left to right: Image classification score on HST, LSST10,
  LSST1 mock observed lensing images as a function of lensed image
  magnification.  Top row: Each panel is color coded by the lens
  velocity dispersion in km/s.  High velocity dispersion lens galaxies
  are likely to produce high magnification images of the source
  galaxies.  Magnification is the strongest indicator of how likely a
  lensing system will be successfully classified.  Bottom row: Here,
  we color code by the redshift of the lens galaxy.}
\label{fig:scorevslensparams}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\acknowledgments CA acknowledges support from the Enrico Fermi
Institute at the University of Chicago, and the University of Chicago
Provost's Office. This work was also supported in part by the Kavli
Institute for Cosmological Physics at the University of Chicago
through grant NSF PHY-1125897 and an endowment from the Kavli
Foundation and its founder Fred Kavli.
\lastpagefootnotes

>>>>

\author{Camille Avestruz\altaffilmark{1-3,$\dagger$}\thanks{E-mail:
    avestruz@uchicago.edu}, Nan Li\altaffilmark{2-4}, Matthew Lightman\altaffilmark{5}, Thomas E.~Collett\altaffilmark{6}, Wentao Luo\altaffilmark{7}}

\affil{
$^1${Enrico Fermi Institute, The University of Chicago, Chicago, IL 60637 U.S.A.}\\
$^2${Kavli Institute for Cosmological Physics, The University of Chicago, Chicago, IL 60637 U.S.A.}\\
$^3${Department of Astronomy \& Astrophysics, The University of Chicago, Chicago, IL 60637 U.S.A.};\\
$^4${High Energy Physics Division, Argonne National Laboratory,
Lemont, IL 60439};\\
$^5${Digital Intelligence, JPMorgan Chase, Chicago, IL 60603 U.S.A.};\\
$^6${Institute of Cosmology and Gravitation, University of Portsmouth, Burnaby Rd, Portsmouth, PO1 3FX, UK};\\
$^7${Center for Astronomy and Astrophysics, Shanghai Jiaotong University,
800 Dongchuan Road, Shanghai 200240, China};\\
$^\dagger${Provost's Postdoctoral Scholar at the University of Chicago}\\
  \href{mailto:avestruz@uchicago.edu}{avestruz@uchicago.edu}\\
}

@@

% Convolutional and residual
The most advanced use of neural networks for strong lensing
classification operate directly in image space.
\citep{petrillo_etal17} used mock Kilo Degree Survey data to train
convolutional neural networks, with a training set size of six million
images. \citet{lanusse_etal17} used state-of-the-art residual learning
to also work directly in the image space with minimal image
pre-processing.  A major strength of the \citet{lanusse_etal17}
implementation is that residual learning has been found to be easier
to train in deep neural networks, and can outperform implementations
of convolutional neural networks.

@@

In a forthcoming paper, we will discuss how class imbalance, or
differences between the lens-model parameter distributions in the
training and test sets affect model performance and will explore a
method to correct for this.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                        
\begin{figure*}[t]
  \centering 
  \mbox{
    \subfigure{\includegraphics[width=.66\columnwidth,trim=13 0 10 0,
        clip]{figures/lens_parameter_dependence/HST_Magnification_Velocity_Dispersion.pdf}}\hfill
    \subfigure{\includegraphics[width=.66\columnwidth,trim=13 0 10 0,
        clip]{figures/lens_parameter_dependence/LSST10_Magnification_Velocity_Dispersion.pdf}}\hfill
    \subfigure{\includegraphics[width=.66\columnwidth,trim=13 0 10 0,
        clip]{figures/lens_parameter_dependence/LSST1_Magnification_Velocity_Dispersion.pdf}\hfill}
  }\\ 
  \mbox{
    \subfigure{\includegraphics[width=.66\columnwidth,trim=13 0 10 0,
        clip]{figures/lens_parameter_dependence/HST_Magnification_z.pdf}}\hfill
    \subfigure{\includegraphics[width=.66\columnwidth,trim=13 0 10 0,
        clip]{figures/lens_parameter_dependence/LSST10_Magnification_z.pdf}}\hfill
    \subfigure{\includegraphics[width=.66\columnwidth,trim=13 0 10 0,
        clip]{figures/lens_parameter_dependence/LSST1_Magnification_z.pdf}\hfill}
  }\\ 
\caption{Left to right: Image classification score on HST, LSST10,
  LSST1 mock observed lensing images as a function of lensed image
  magnification.  Top row: Each panel is color coded by the lens
  velocity dispersion in km/s.  High velocity dispersion lens galaxies
  are likely to produce high magnification images of the source
  galaxies.  Magnification is the strongest indicator of how likely a
  lensing system will be successfully classified.  Bottom row: Here,
  we color code by the redshift of the lens galaxy.}\vspace{10pt}
\label{fig:scorevslensparams}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\acknowledgments CA acknowledges support from the Enrico Fermi
Institute at the University of Chicago, and the University of Chicago
Provost's Office. This work was also supported in part by the Kavli
Institute for Cosmological Physics at the University of Chicago
through grant NSF PHY-1125897 and an endowment from the Kavli
Foundation and its founder Fred Kavli.  NL would like to thank the
funding support from NSFC, grant no.11503064, and Shanghai Natural
Science Foundation, grant no. 15ZR1446700.
\lastpagefootnotes
